\section*{Conference Presentations}
\vspace{\postsubhead}
\begin{adjustwidth}{\indentleft}{\indentright}
 \begin{itemize}
    \setlength\itemsep{0.5em}
    
    \item \textbf{Avery Ma}, Nikita Dvornik, Ran Zhang, Leila Pishdad, Konstantinos G. Derpanis, Afsaneh Fazly (2022). SAGE: Saliency-Guided Mixup with Optimal Rearrangements. \textbf{Poster Presentation} at the \emph{33rd British Machine Vision Conference}. London, UK
    
    \item \textbf{Avery Ma}, Simona Meng, Amir-massoud Farahmand (2021). Adversarial Robustness through the Lens of Fourier Analysis. \textbf{Poster Presentation} at the \emph{Vector Rsearch Symposium}. Vector Institute, Toronto, Ontario
    
    \item \textbf{Avery Ma}, Amir-massoud Farahmand (2019). Adversarial Robustness using Taylor Series-based Regularizer. \textbf{Poster Presentation} at the \emph{Evolution of Deep Learning Symposium}. Vector Institute, Toronto, Ontario
    
    \item \textbf{Avery Ma}, Amir-massoud Farahmand (2018). Adversarial Robustness Through Loss regularization. \textbf{Poster Presentation} at the \emph{Vector Research Symposium}. Vector Institute, Toronto, Ontario
    
    \item \textbf{Avery Ma}, Ahmed Gawish, Mark Lamm, Alexander Wong, Paul Fieguth (2018). Real-time Spatial-based Projector Resolution Enhancement. \textbf{Oral Presentation} at the \emph{Society for Information Display - Display Week 2018}. Los Angeles Convention Center, Los Angeles, California
    
    \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2018). Deep Learning-driven Depth from Defocus via Active Multispectral Quasi-random Projections with Complex Subpatterns. \textbf{Poster Presentation} at the \emph{15th Conference on Computer and Robot Vision}. York University, Toronto, Ontario
            
    \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2017). Depth from Defocus via Active Multispectral Quasi-random Point Projections using Deep Learning. \textbf{Oral Presentation} at the \emph{3rd Annual Conference on Vision and Imaging Systems}. University of Waterloo, Waterloo, Ontario.
    
    \item Xiaodan Hu, \textbf{Avery Ma}, Ahmed Gawish, Mark Lamm, Paul Fieguth (2017). Motion Detection in High Resolution Enhancement. \textbf{Poster Presentation} at the \emph{3rd Annual Conference on Vision and Imaging Systems}. University of Waterloo, Waterloo, Ontario.
    
    \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2017). Depth from Defocus via Active Quasi-random Point Projections: a Deep Learning Approach. \textbf{Poster Presentation} at the \emph{14th International Conference on Image Analysis and Recognition}. Polytechnique Montréal, Montreal, Quebec
    
    \item \textbf{Avery Ma}, Alexander Wong (2017). Enhanced Depth from Defocus via Active Quasi-random Colored Point Projections. \textbf{Oral Presentation} at the \emph{9th International Conference on Inverse Problems in Engineering}. University of Waterloo, Waterloo, Ontario.
    
    \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2016). Depth from Defocus via Active Multispectral Quasi-random Point Projections using Deep Learning. \textbf{Poster Presentation} at the \emph{2nd Annual Conference on Vision and Imaging Systems}. University of Waterloo, Waterloo, Ontario
\end{itemize}
\end{adjustwidth}
