\section*{Publications}
    \vspace{\postsubhead}
    \begin{adjustwidth}{\indentleft}{\indentright}
        \begin{itemize}
            \setlength\itemsep{0.6em}

            \item \textbf{Avery Ma}, Amir-massoud Farahmand, Yangchen Pan, Philip Torr, Jindong Gu (2024). Improving Adversarial Transferability via Model Alignment. \emph{ECCV'24: European Conference on Computer Vision}.

            \item Jindong Gu, Xiaojun Jia, Pau de Jorge, Wenqian Yu, Xinwei Liu, \textbf{Avery Ma}, Yuan Xun, Anjun Hu, Ashkan Khakzar, Zhijiang Li, Xiaochun Cao, Philip Torr (2023). A Survey on Transferability of Adversarial Examples Across Deep Neural Networks. \emph{TMLR: Transactions on Machine Learning Research}.
            
            \item \textbf{Avery Ma}, Yangchen Pan, Amir-massoud Farahmand (2023). Understanding the robustness difference between stochastic gradient descent and adaptive gradient methods. \emph{TMLR: Transactions on Machine Learning Research (\textbf{Featured Certification (Top 3\%}), ICLR'24 Journal-to-Conference}).
            
            \item \textbf{Avery Ma}, Nikita Dvornik, Ran Zhang, Leila Pishdad, Konstantinos G. Derpanis, Afsaneh Fazly (2022). SAGE: Saliency-Guided Mixup with Optimal Rearrangements. \emph{BMVC'22: British Machine Vision Conference}.
            
            \item \textbf{Avery Ma}, Aladin Virmaux, Kevin Scaman, Juwei Lu (2021). Improving Hierarchical Adversarial Robustness of Deep Neural Network. \emph{arXiv preprint arXiv: 2102.09012}.
            
            \item \textbf{Avery Ma}, Fartash Faghri, Nicolas Papernot, Amir-massoud Farahmand (2020). SOAR: Second-Order Adversarial Regularization. \emph{arXiv preprint arXiv: 2004.01832} .
            
            \item Plinio Morita, Adson Rocha, George Shaker, Dave Lee, Jing Wei, Brandon Fong, Anjali Thatte, Amir Karimi, Linlin Xu, \textbf{Avery Ma}, Alexander Wong, Jennifer Boger (2020). Comparative Analysis of Gait Speed Estimation Using Wideband and Narrowband Radars, Thermal Camera, and Motion Tracking Suit Technologies. \emph{Journal of Healthcare Informatics Research}.
            
            \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2018). Deep Learning-driven Depth from Defocus via Active Multispectral Quasi-random Projections with Complex Subpatterns. \emph{CRV'18: Conference on Computer and Robot Vision}.
            
            \item \textbf{Avery Ma}, Ahmed Gawish, Mark Lamm, Alexander Wong, Paul Fieguth (2018). Real-time Spatial-based Projector Resolution Enhancement. \emph{SID'18: Society for Information Display}.
            
            \item \textbf{Avery Ma}, Alexander Wong (2018). An Inverse Problem Approach to Computational Active Depth from Defocus. \emph{Journal of Physics: Conference Series}.
            
            \item Xiaodan Hu, \textbf{Avery Ma}, Ahmed Gawish, Mark Lamm, Paul Fieguth (2017). Motion Detection in High Resolution Enhancement. \emph{CVIS'17: Conference on Vision and Imaging Systems}.
            
            \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2017). Depth from defocus via active multispectral quasi-random point projections using deep learning. \emph{CVIS'17: Conference on Vision and Imaging Systems}.
            
            \item \textbf{Avery Ma}, Alexander Wong, David Clausi (2017). Depth from Defocus via Active Quasi-random Point Projections: a Deep Learning Approach. \emph{ICIAR'17: International Conference on Image Analysis and Recognition}.
            
            \item \textbf{Avery Ma}, Alexander Wong (2017). Enhanced Depth from Defocus via Active Quasi-random Colored Point Projections. \emph{ICIPE'17: International Conference on Inverse Problems in Engineering}.
                   
            \item \textbf{Avery Ma}, Francis Li, Alexander Wong (2016). Depth from Defocus via Active Quasi-random Point Projections. \emph{CVIS'16: Conference on Vision and Imaging Systems}.
       
        \end{itemize}
        \hfill
        % \textit{*: Peer-reviewed}
        
        
 
        
    \end{adjustwidth}
    % \vspace{\postsection}